\part{Search for Flavor-Violating e$\bm{\upmu}$qt Interactions}
\label{Part3}
The \autoref{Part3} of this thesis documents a physics analysis that was performed in 2020-2023 using data collected by the \ac{CMS} detector in 2016-2018. This analysis was made public in February 2023~\cite{CMS:2023phe} and was largely done by myself with the advice from Prof. Skinnari and technical support provided centrally by the \ac{CMS} Collaboration. The \autoref{Part3} is organized as follows. \autoref{chap:History} gives a brief overview of this analysis as well as all past \ac{CLFV} searches in the top quark sector performed at the \ac{ATLAS} and \ac{CMS} experiments. \autoref{chap:Samples} describes the datasets, simulated samples, and triggers used by this analysis. Object- and event-level selection criteria are described in \autoref{chap:Objects} and \autoref{chap:Selection}, respectively. Treatments of the \emph{nonprompt} backgrounds and signal extraction using \ac{BDT} are described in \autoref{chap:Nonprompt} and \autoref{chap:BDT} respectively. Finally, the systematic uncertainties that affect this analysis and statistical interpretation of the results are described in \autoref{chap:Systematics} and \autoref{chap:Results}, respectively. Except where noted, materials presented in the \autoref{Part3} are prepared by myself.
\input{chapters/Part3/History}
\input{chapters/Part3/Samples}
\input{chapters/Part3/Objects}
\input{chapters/Part3/Selection}
\input{chapters/Part3/Nonprompt}
\input{chapters/Part3/BDT}
\input{chapters/Part3/Systematics}
\input{chapters/Part3/Results}