\begin{acknowledgments}

Confucius says: ``Is it not delightful to have friends coming from afar?'' I am glad that I received a few visits from my brother during my graduate study. When we were not together, we spent a lot of time on the phone talking about all the happy and sad things that happened in the world. He was the ``closest'' person in my family and my best friend. I could not have made it this far without his moral support.

I am incredibly grateful to Louise who took me as her first student at a time when I was really unsure about the direction of my life. I imagined it would not be an obvious decision for most PIs given that I had no prior experience in the field. She always respected and supported the way I approach my research while deeply caring about my growth as a researcher. I am forever in her debt.  

I would like to express my gratitude to members of the Northeastern HEP community, especially Ela and Toyoko. I learned about particle physics from Ela. Her enthusiastic and insightful lectures truly captured my heart and inspired me to pursue an adventure in particle physics. Toyoko reached out to me many times to hear about my life story and share hers with me, and it means a lot to me.

Special thanks go to my parents and grandparents, who never forgot to send me their encouraging words when I needed the most. Despite not receiving much formal education themselves, they value my education above all else and are always curious about everything I do. I love you!

With COVID-19 and constantly moving in foreign countries, it was hardly easy for me to have a ``normal'' graduate school experience. In this regard, I would like to thank Bingran who helped me in many ways when I relocated to CERN. I would also like to thank Amrutha, Meng, Nick, and Yixiao who were willing to get together for my rather random and sometimes silly initiatives/activities, which really matter to me. I regard them as both supportive colleagues and my friends during my stay at CERN.

Thank you to Emily who has made invaluable contributions to the analysis work presented in this thesis. I have always appreciated her dedication and bright ideas. The lack of in-person interaction and my ambiguous English language did not prevent a fruitful collaboration between us. I cherish my relatively short but wonderful experience working with her even though we have yet to meet in real life.

\end{acknowledgments}